Implementing simplified INLA into `aghq`

### 2022-10-25 src/dev_sinla/sinla.Rmd
Add clean version script #16

```{r}
i <- 1
mean_i <- as.numeric(mean[i])
var_i <- solve(Q)[i, i]
```

>>>>

```{r}
#' Making sure the mean and Q used here are correct (preventing and shady TMB behaviour)
h$fn(opt_theta)
mm <- h$env$last.par
mean <- mm[h$env$random]
Q <- h$env$spHess(mm, random = TRUE)

i <- 1
mean_i <- as.numeric(mean[i])
var_i <- solve(Q)[i, i]
```
